NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-11 paper/Chapters/Chapter2.tex
introduction almost done

\begin{itemize}
	\item Total energy intake = (protein(gramme) $\times$ 17) + (fat(gramme) $\times$ 37) + (carbohydrate(gramme) $\times$ 16) + (alcohol(gramme) $\times$ 29)  kJ;
	\item Carbohydrate intake = total sugars (gramme) + starch (gramme); 
%	\item Total sugars = sum of all individual sugars (gramme).
\end{itemize}

>>>>

\begin{itemize}
	\item Total energy intake = (protein(gram) $\times$ 17) + (fat(gram) $\times$ 37) + (carbohydrate(gram) $\times$ 16) + (alcohol(gram) $\times$ 29)  kJ;
	\item Carbohydrate intake = total sugars (gram) + starch (gram); 
%	\item Total sugars = sum of all individual sugars (gramme).
\end{itemize}
